---
title: "Leave-One-Out-CV"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Leave-One-Out-CV}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, include = F}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.height = 4,
  fig.width = 7.5
)
```
```{r setup, include = F}
library(PSplinesR)
par(cex.axis = 1.5, cex.lab = 1.5)
```

Here, we consider the data provided in this package `EgData129`. See `?EgData129` for more information on this data.

```{r, ShowData}
x <- EgData65$x
y <- EgData65$y

plot(x, y, pch = 4)
lines(x, sin(x), col = 2)
```

---

Due to the lack of speed of the LOOCV function we look at CV error at sparse
points on the log scale

```{r, LogScale}
PSplinesR::MinimiseLOOCV(x, y, c(0.01, 0.1, 1, 10, 100, 1000, 10000), FALSE)
```

---

We got the minimum value 100, using this initial information, we can obtain 
the optimal smoothing parameter to a specified degree of accuracy.

```{r, Iter1}
PSplinesR::MinimiseLOOCV(x, y, c(1, seq(100, 1000, 100)))
```
```{r, Iter2}
PSplinesR::MinimiseLOOCV(x, y, seq(10, 190, 10))
```
```{r, Iter3}
PSplinesR::MinimiseLOOCV(x, y, seq(51, 69, 1))
```
```{r, Iter4}
minVal <- PSplinesR::MinimiseLOOCV(x, y, seq(62.1, 63.9, 0.1))
print(minVal)
```

---

This smoothing parameter is the minimiser of the CV error (to 3.s.f.).

Hence, this value of smoothing parameter leads to the optimal fitted values in
regard to the bias variance trade-off.

We plot these fitted values alongside some other fitted values generated from
different smoothing parameters alongside the original data.

```{r, fig.height=8}
par(mfrow=c(2,2))
for(LamI in c(10^(-3), minVal, 10^3, 10^6)) {
  CVI <- round(PSplinesR::CalculateLOOCV(x, y, LamI), 4)
  PSplinesR::PlotPSplineFit(x, y, LamI,
                            main = paste("Smooth =", LamI, " CV =", CVI))
}
```
